---
title: "Open Research Survey Report"
author: "Emma Wilson"
date: "22/02/2021"
output: 
    html_document:
      theme: cosmo
---

```{r data-select, include=FALSE}
datSource <- c("Medical Research Council (MRC)-funded institutions", "The University of Bristol", "The Babraham Institute")
```


```{r logo, echo=FALSE}
htmltools::img(src = knitr::image_uri(file.path("logo.jpg")), 
               alt = 'UKRN logo', 
               style = 'position:absolute; top:0; right:0; padding:25px 250px;')
```

---

```{r setup, include=FALSE}
# R packages
library(tidyverse)    # Tivdyverse packages
# Functions
source("functions/format_distribution.R") # Create a histogram of responses
source("functions/format_leadership.R")   # Format MajorleadershipRole for graph
source("functions/format_priority.R")     # Format OR area priority responses
source("functions/format_training.R")     # Format training responses for graph
source("functions/read_survey.R")         # Read in and format survey data
# KnitR
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r data, include=FALSE}
# Clean column text
col_order <- read_csv("data-helpers/colOrder.csv")
# MRC taxonomy
mrc_group <- read_csv("data-helpers/mrcTaxonomy.csv")
# Survey data
# Read in survey data
dat_mrc <- read_survey("data", "MRC") # MRC-funded institutions
dat_uob <- read_survey("data", "UoB") # University of Bristol
dat_bab <- read_survey("data", "Babraham") # Babraham Institute
#Bind into one dataframe
dat <- rbind(dat_mrc, dat_uob, dat_bab)

#clear environment
rm(col_order, dat_bab, dat_mrc, dat_uob, mrc_group)
```

# Survey Data
<!-- Tidy up this section so it's neater -->
This report summarises survey responses from `r datSource[1]`, `r datSource[2]`, and `r datSource[3]`.
A total of **`r nrow(dat)**` researchers responded to this survey.

  * **`r nrow(dat %>% filter(Unit == "MRC"))`** (`r round((nrow(dat %>% filter(Unit == "MRC"))/nrow(dat))*100)`%) from `r datSource[1]`
  * **`r nrow(dat %>% filter(Unit == "UoB"))`** (`r round((nrow(dat %>% filter(Unit == "UoB"))/nrow(dat))*100)`%) from `r datSource[2]`
  * **`r nrow(dat %>% filter(Unit == "Babraham"))`** (`r round((nrow(dat %>% filter(Unit == "Babraham"))/nrow(dat))*100)`%) from `r datSource[3]`
