---
title: "Open Research Survey <img src=\"logos/UKRN_logo.jpg\" alt=\"UKRN logo\" style = \"float: right; padding-left: 20px;\"/><img src=\"logos/MRC_logo.png\" alt=\"MRC logo\" style = \"float: right; padding-left: 20px;\"/><img src=\"logos/UoB_logo.png\" alt=\"University of Bristol logo\" style = \"float: right; padding-left: 20px;\"/>"
author: "Emma Wilson"
date: "`r Sys.Date()`"
output: 
    html_document:
      theme: cosmo
---

```{r select, include=FALSE}
# Choose the data to run the report on
choose <- c("all", "mrc", "uob", "babraham")[1]
```

---

```{r setup, include=FALSE}
# R packages
library(forcats)      # For factor reverse
library(grid)         # Plot arrangement
library(gridExtra)    # Plot arrangement
library(tidyverse)    # Tidyverse packages
# Icons
#remotes::install_github("mitchelloharawild/icons")
library(icons)
#download_fontawesome()
#download_academicons()
# Functions
source("functions/format_distribution.R")       # Create a histogram of responses
source("functions/format_leadership.R")         # Format leadership
source("functions/plots.R")                     # Generate plots
source("functions/format_priority.R")           # Format OR area priority responses
source("functions/format_priority_training.R")  # Format OR area priority responses (subset)
source("functions/format_training.R")           # Format training responses for graph
# KnitR
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r data, include=FALSE}
# Read in data
dat <- read_csv("data/survey_data.csv")

# Change OpenData --> DataSharing
colnames(dat) <- gsub("OpenData", "DataSharing", colnames(dat))

# Select relevant data
if(choose == "all"){
  dat <- dat
} else if(choose == "mrc"){
  dat <- filter(dat, Unit == "MRC")
} else if(choose == "uob"){
  dat <- filter(dat, Unit == "UoB")
} else if(choose == "babraham"){
  dat <- filter(dat, Unit == "Babraham")
}
```

```{r fuction-format, include=FALSE}
# Leadership graph
dat <- format_leadership(dat)

# Subset and format responses from those who would or wouldn't find training useful
dat_training <- format_training_familiarity(dat, training = "Yes")
dat_no_training <- format_training_familiarity(dat, training = "No")

# Bind datasets together
dat_all_training <- rbind(dat_training, dat_no_training) %>%
  select(OR_Area, Response, Training)

# Factor levels
dat_all_training$Response <- factor(dat_all_training$Response,
                                    levels = c("Unknown familiarity",
                                               "Not familiar",
                                               "Familiar",
                                               "Already engage"))

# Institution provides training
dat_training_provided <- format_training_provided(dat)

# Create dataframe of topics ranked by priority
priority <- format_priority(dat)

# Subset only responses from those who would find training useful
priority_training <- format_priority_training(priority, dat_training)
```

```{r function-plots, include=FALSE}
p1 <- plot_responsesovertime(dat) # Responses over time (Figure 1)
p2_a <-plot_discipline(dat) # Discipline (Figure 2a)
p2_b <- plot_leadership(dat) # Leadership (Figure 2b)
p3 <- plot_training(dat_all_training, dat) # Training and familiarity (Figure 3)
p4 <- plot_training_provided(dat_training_provided, dat) # Training provided (Figure 4)
p5 <- plot_priority(priority) # Priority rank (Figure 5)
p6 <- plot_priotity_training(priority_training, priority) # Priority rank of training useful only (Figure 6)
```

# 1. Aim
This survey aimed to investigate the engagement of health and life sciences researchers with open research practices and training. The results of this survey will be used to inform priorities for researcher training in five different open research areas:

  * Open access publishing
  * Sharing of code and materials
  * Data sharing
  * Publishing preprints
  * Preregistration and registered reports

# 2. Survey data

```{r echo=FALSE, results="asis", warning=FALSE, message=FALSE}
# Number of responses text
if(choose == "all"){
  cat('This report summarises', nrow(dat), 'survey responses from life and health sciences researchers at Medical Research Council (MRC)-funded institutions, The University of Bristol, and The Babraham Institute.\n\n')
} else if(choose == "mrc"){
  cat('This report summarises', nrow(dat), 'survey responses from life and health sciences researchers at Medical Research Council (MRC)-funded institutions.\n\n')
} else if(choose == "uob"){
  cat('This report summarises', nrow(dat), 'survey responses from life and health sciences researchers at The University of Bristol.\n\n')
} else if(choose == "babraham"){
  cat('This report summarises', nrow(dat), 'survey responses from life sciences researchers at The Babraham Institute.\n\n')
} else {
  cat('Error: Please choose a valid data breakdown.')
}
```

## 2.1 Survey dissemination

```{r, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
# Dissemination text
if(choose == "all"){
  cat('MRC researchers were reached via MRC Institution leads. A central MRC response strongly encouraged responding, and several Institutes were given personal follow-up by the project steering group members. University of Bristol researchers were reached via department heads. Babraham Institute researchers were reached via their institute head.\n\n')
} else if(choose == "mrc"){
  cat('MRC researchers were reached via MRC Institution leads. A central MRC response strongly encouraged responding, and several Institutes were given personal follow-up by the project steering group members.\n\n')
} else if(choose == "uob"){
  cat('University of Bristol researchers were reached via department heads.\n\n')
} else if(choose == "babraham"){
  cat('Babraham Institute researchers were reached via their institute head.\n\n')
} else {
  cat('Error: Please choose a valid data breakdown.')
}
```

## 2.2 Survey Responses
Survey responses were collected between January and February 2021. Most responses were received in January (Fig 1).

```{r, echo=FALSE}
# Plot responses over time
p1
```

<em><b>Figure 1: Number of responses over time.</b></em>

## 2.3 Respondent demographics
Survey respondents were asked to self-report which organisation they belonged to and if they had a leadership role within their organisation. A major leadership role was defined as running a group/lab, directing a school/organisation, or similar.

```{r, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
#Demographics plots and captions
if(choose == "all"){
  cat('Most responses came from MRC-funded institutes and researchers in the health sciences domain (Fig 2a). Additionally, most survey respondents did not have a major leadership role (Fig 2b).\n\n')
  grid.arrange(p2_a, p2_b, nrow = 1, widths = c(4, 2))
  cat('\n\n<em><b>Figure 2: Breakdown of survey responses</b> by organisation and research discipline (a) and by leadership role (b).</em>\n\n')
} else if(choose == "mrc"){
  cat('Most responses came from researchers in the population and public health and health sciences domain (Fig 2a). Additionally, most survey respondents did not have a major leadership role (Fig 2b).\n\n')
  grid.arrange(p2_a, p2_b, nrow = 1, widths = c(4, 2))
  cat('\n\n<em><b>Figure 2: Breakdown of survey responses</b> by research domain taxonomy and discipline (a) and by leadership role (b).</em>\n\n')
} else if(choose == "uob"){
  cat('Most responses came from researchers in the health sciences domain (Fig 2a). Additionally, most survey respondents did not have a major leadership role (Fig 2b).\n\n')
  grid.arrange(p2_a, p2_b, nrow = 1, widths = c(2, 2))
  cat('\n\n<em><b>Figure 2: Breakdown of survey responses</b> by research discipline (a) and by leadership role (b).</em>\n\n')
} else if(choose == "babraham"){
  cat('Most survey respondents did not have a major leadership role (Fig 2).\n\n')
  grid.arrange(p2_b, nrow = 1, widths = c(2))
  cat('\n\n<em><b>Figure 2: Breakdown of survey responses from researchers by leadership role.</b></em>\n\n')
} else {
  cat('Error: Please choose a valid data breakdown.')
}
```

# 3. Open research training
Survey respondents were asked to describe their familiarity with the five open research areas, and whether they thought the training would be useful.

```{r, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
# Dissemination text
if(choose == "all"){
  cat('Most respondents would find training in data sharing useful (Fig 3). Additionally, the majority of survey respondents were familiar or already engaged in open access and data sharing practices, however a large proportion were not familiar with open code and preregistration.\n\n')
} else if(choose == "mrc"){
  cat('Most respondents would find training in data sharing useful (Fig 3). Additionally, the majority of survey respondents were familiar or already engaged in open access, data sharing, and publishing preprints. However a large proportion were not familiar with open code and preregistration.\n\n')
} else if(choose == "uob"){
  cat('Most respondents would find training in data sharing useful (Fig 3). Additionally, the majority of survey respondents were familiar or already engaged in open access, data sharing, and publishing preprints. However a large proportion were not familiar with open code and preregistration.\n\n')
} else if(choose == "babraham"){
  cat('Most respondents would find training in data sharing useful (Fig 3). Additionally, the majority of survey respondents were familiar or already engaged in open access, data sharing, and publishing preprints. However a large proportion were not familiar with open code and preregistration.\n\n')
} else {
  cat('Error: Please choose a valid data breakdown.')
}
```

```{r training-plot, echo=FALSE}
# Plot training and familiarity
p3
```

<em><b>Figure 3: Breakdown of responses related to training in the five open research areas.</b> Respondents could select from multiple answers, so responses were coded as follows: respondents who said they were both familiar and engaged in an open research area were marked as 'Already engage'. Respondents who did not state their familiarity were marked as 'Unknown familiarity'.</em>

## 3.1 Training already provided
In the same survey question as the previous, survey respondents were asked if they thought their institution provided sufficient training in each open research area. Very few respondents said they did (Fig 4).

```{r training-provided-plot, echo=FALSE}
# Plot training provided
p4
```

<em><b>Figure 4: Respondents who thought sufficient training already provided by institution.</b></em>

# 4. Priority of training topics
Survey respondents were asked which open research areas they thought should be most prioritised for researcher training. To do this, they were asked to rank the five open research areas we had suggested (open access, open code, data sharing, preprints and preregistration) and could suggest an additional three open research areas in an optional free-text field. Only `r length(unique(priority$randomID))` respondents completed this section.

Out of the five open research areas, data sharing was ranked the number one priority for researcher training by the most survey respondents (Fig 5).

```{r priority-plot, echo=FALSE}
# Plot priority rank
p5
```

<em><b>Figure 5: Priority ranking of each of the five open research areas.</b> 1 is the highest priority and 8 is the lowest. Where an area has been ranked 6-8, the number of responses is aggregated.</em>

The distribution of priority rankings across the five research areas is retained when only responses from researchers who would find training in each area useful were considered (Fig 6).

```{r priority-training-plot, echo=FALSE}
# Plot priority rank of only those who would find training useful
p6
```

<em><b>Figure 6: Priority ranking of each of the five open research areas from only the respondents who would find training in each area useful.</b> 1 is the highest priority and 8 is the lowest. Where an area has been ranked 6-8, the number of responses is aggregated.</em>

## 4.1 Suggested additional open research areas
In the survey, respondents could suggest up to three additional open research areas not covered by open access, open code, data sharing, preprints, and preregistration. Respondents suggested and ranked within their top five priority training areas, the following additional open research areas:

  * **Legal, ethics and governance** -- this training might be relevant for senior researchers and organisation managers, and could address the call for training lead researchers on the value of open research practices.
  * **Experimental design** -- this training could be considered as part of a primer series or background information related to the research workflow.

# 5. Summary of free-text responses
The final section of this report presents a summary of the free-text fields in the survey. Respondents could enter free-text to suggest additional topics for training and additional contents for existing topics. They could also explain their suggestions and add further information for each topic. These free-text responses were reviewed by two people who identified the key themes and agreed on the summary presented below.

The responses are from health and life sciences researchers across the University of Bristol, MRC-funded organisations, and the Babraham Institute, and may not reflect the views of researchers at any particular organisation. Responses were grouped into seven key areas:

  * Culture, leadership and institutional requirements
  * Systemic issues, e.g. funding and publishing models
  * Confusion over open research terms
  * Workshop contents
  * Workshop structure and design
  * Workshop audiences
  * Challenges and worthwhileness

## 5.1 Culture, leadership and institutional requirements
Many responses complained of a lack of institutional or direct managerial leadership, or of a culture where open research was not valued. Respondents requested that their institutions provided: a) guidance on licensing, archiving data, etc.; b) direct financial support for e.g. sharing data.; c) policies endorsing the use of free and open software tools; and d) training on open research practices. Several respondents requested that project leaders be specifically trained in open research methods so that they could appreciate the value and accept the time taken to implement them. Some respondents praised institutional leadership where it supported Open Access publishing. Some respondents showed that institution induction processes overlooked open research practices as a component in the on-boarding process.

## 5.2 Systemic issues
Many responses complained that open research practices take time to implement, that they have limited time to attend training courses, and that open research practices are not incentivised by funders, publishers, or their institutions. Several responses also said that open research practices can be costly e.g. open access publishing, but they do not want to fund closed-access journals.

## 5.3 Confusion over open research terms
Some respondents appeared confused by the terms used in the survey - particularly 'open code', which we defined as applying to materials and formalised procedures other than computer software, but which were understandably interpreted differently.

## 5.4 Workshop contents
In general, respondents would like workshops to cover specific types of research, using specific examples and providing templates that researchers can use to put their learning into practice. Many respondents feel that, of the currently available open research workshops they have access to, information on how to implement open research practices to projects using qualitative data is neglected. In relation to open access publishing, respondents would like to know about plan-S and identifying appropriate journals and funding routes. In open code workshops, respondents would like to learn about accessible tools, e.g. Python over paid-for tools like MATLAB), licensing and how much code to make public. For data sharing, respondents would like workshops to cover the different types of repositories available to them, legislation such as GDPR, guidance on data management plans, and to what extent they can practice data sharing if they would with restricted or sensitive data. In relation to preprints, respondents wanted information on the impact publishing preprints has on journal publishing, and if DOIs can carry through from preprint to full publication. Finally, respondents would like preregistration workshops to cover the tradeoffs between preregistering and prematurely disclosing research ideas and avoiding the discouragement of data exploration.

## 5.5 Workshop structure and design
There was some support for training that provided specific step-by-step guidance rather than training that raised awareness of a practice. Specific, practical training was requested.

## 5.6 Workshop audience
Many respondents believed they would get more benefit from training workshops targeted to a specific type of research, e.g. research using qualitative data or restricted data. Several respondents expressed that training might be more relevant to early career researchers and PhD students, who will be doing most of the practical work in a research project, and less relevant to supervisors and PIs. However, several respondents also suggested that they would like to see a top-down approach to implementing open research practices within research groups or organisations, which would require senior researchers to understand and value these practices. 

## 5.7 Challenges and worthwhileness
Some respondents challenged the worthwhileness of some of our training topics, mostly challenging the usefulness of preregistration to discovery-based science. 

---

[`r fontawesome("github")` &nbsp; GitHub repository](https://github.com/UKRN-Open-Research/survey-reports) &nbsp;&nbsp; | &nbsp;&nbsp; `r academicons("open-data")` &nbsp; Survey data